\textbf{\sc Towards Deliberative Control in Marine Robotics}

### 2012-06-06 final-version/europa-basics.tex
updates to final version

Planning as an activity is ingrained in human decision-making
\cite{berthoz} and its generalization into a computational framework
demonstrating machine intelligence \kcomment{has for long been}
targeted by pioneers in computer science
\cite{computersthought}. Early work in this context focused on logical
theorem proving by computer \cite{green69} which has formed the basis
of much of the discipline. The emphasis in these early efforts was to
logically derive the existence proof of a trajectory of actions for a
hypothetical robot (moving blocks, chess pieces, furniture etc) to
achieve a specific goal given specific initial conditions. Two
important properties of \emph{Soundness}\footnote{A planning algorithm
  is \emph{sound} if invoked on a problem $P$ returns a plan which is
  a solution for $P$.} and \emph{Completeness}\footnote{A planning
  algorithm is \emph{complete} if invoked on a solvable problem $P$ is
  guaranteed to return a solution.} along with derived results for
algorithmic complexity \cite{gareyjohnson,corman} were a defining
cornerstone for understanding how different computational paradigms
could actually be tractable first in simulation and subsequently in
actual robotic platforms. In this chapter our emphasis is to focus on
embedded AI Planning and the execution of plans on an embedded
\kcomment{marine robotic} platform. The techniques we highlight are
general purpose as noted in Section \ref{sec:intro}.

\begin{figure}[b]
\centering
  \includegraphics[scale=3]{figs/shopping_europa.jpeg}
  \caption{\small A potential plan for a robot shopping for groceries.}
\label{fig:shop:shopping}
\end{figure}

@@

{\small
  \begin{quote}
    In the near future, a personal robot sets out to buy a gallon of
    milk. This involves a number of tasks: obtain keys, obtain wallet,
    start car, drive to store, find and obtain milk, purchase milk,
    etc.  The embedded planner has to have a ``model'' of the world in
    which it 'lives' and has to use the task primitives in this model
    to structure the actions so it achieves its goal. Constraints
    control when certain tasks can or cannot occur. For example the
    robot must obtain the keys and wallet \emph{before} driving to the
    store and pick up the milk \emph{before} purchasing it.
\end{quote}

>>>>

Planning as an activity is ingrained in human decision-making
\cite{berthoz} and its generalization into a computational framework
demonstrating machine intelligence \kcomment{has for long been}
targeted by pioneers in computer science
\cite{computersthought}. Early work in this context focused on logical
theorem proving by computer \cite{green69} which has formed the basis
of much of the discipline. The emphasis in these early efforts was to
logically derive the existence proof of a trajectory of actions for a
hypothetical robot (moving blocks, chess pieces, furniture etc) to
achieve a specific goal given specific initial conditions. Two
important properties of \emph{Soundness}\footnote{A planning algorithm
  is \emph{sound} if invoked on a problem $P$ returns a plan which is
  a solution for $P$.} and \emph{Completeness}\footnote{A planning
  algorithm is \emph{complete} if invoked on a solvable problem $P$ is
  guaranteed to return a solution.} along with derived results for
algorithmic complexity \cite{gareyjohnson,corman} were a defining
cornerstone for understanding how different computational paradigms
could actually be tractable first in simulation and subsequently in
actual robotic platforms. In this chapter our emphasis is on AI
Planning and plan execution on an embedded \kcomment{marine robotic}
platform. The techniques we highlight are general purpose as noted in
Section \ref{sec:intro}.

\begin{figure}[!t]
\centering
  \includegraphics[scale=3]{figs/shopping_europa.jpeg}
  \caption{\small A potential plan for a robot shopping for groceries.}
\label{fig:shop:shopping}
\end{figure}

@@

{\small
  \begin{quote}
    In the near future, a personal robot sets out to buy a gallon of
    milk. This involves a number of tasks: obtain keys, obtain wallet,
    start car, drive to store, find and obtain milk, purchase milk,
    etc.  The embedded planner has to have a ``model'' of the world in
    which it ``lives'' and has to use the task primitives in this
    model to structure the actions so it achieves its
    goal. Constraints control when certain tasks can or cannot
    occur. For example the robot must obtain the keys and wallet
    \emph{before} driving to the store and pick up the milk
    \emph{before} purchasing it.
\end{quote}
